### 2014-11-04 thesis/results/results.tex
Final version of thesis

Recall that $k$-NN with 1 nearest neighbour and C4.5 wrapper feature
selection produced the best accuracy (77.81\%) for the trauma data set, and
logistic regression with correlation coefficient feature selection at a
threshold of 0.1 gave the best AUC (0.846). These two feature selection
methods selected 11 and 29 features respectively, and the features that
were chosen in common between them were: \texttt{operation}, \texttt{bp},
\texttt{iss}, \texttt{lowerlimbnopelvis}, \texttt{age}, \texttt{lowerlimbany}
and \texttt{icu}. This adds evidence to the work of Dinh et al. who found
that \texttt{iss}, \texttt{age} and \texttt{operation} were important
distinguishers of LOS $\leq$ or $>$ 2 days \cite{Dinh2013a}. We also
confirm the findings of Gabbe et al. who found that \texttt{age},
\texttt{iss} and \texttt{bp} were useful in predicting the length of
hospital stay of blunt trauma patients \cite{Gabbe2005}. Our feature
selection results also
support the findings of McGonigal et al. \cite{McGonigal1993} who used
\texttt{age} and
\texttt{iss} to predict the probability of survival for trauma patients, a
related problem in the same medical domain.
Our observations suggest the use of feature selection not only as a
pre-processing step to improve the accuracy or AUC of a classifier, but also
as a tool used separately that could help extract insights from medical data.

@@

There are a number of results which are notable, however. Logistic regression
and K*
were still able to achieve a mean AUC of 0.994 with features selected using
information gain at a 0.05 threshold. This meant that it only used 8 out of
the original 14 features, cutting down the number of features by nearly half.
We mentioned that the MLP had the highest discriminating ability when used with
CFS and C4.5 wrapper selection, with AUC 0.983 and 0.992 respectively. While
this is not as high as the best result of 0.994, it is worth pointing out that
CFS only selected 2 features and C4.5 wrapper, 4 features. This means that
using only 2 features, we were still able to discriminate between the two LOS
classes almost as well as if we used all of the features. Moreover, using
only 6 out of 14 features and $k$-NN with 1 or 20 nearest neighbours, we can
still achieve an accuracy that is less than 1\% worse than the best result
of 98.23\%.

@@

Out of all four automatic feature selection methods, the single feature that
was deemed to be the most important in predicting LOS was \texttt{EpisodeType}.
Although this was a general hospital-wide data set, the importance of this
attribute indicates that condition-specific factors should be taken into
account when predicting the LOS for any medical domain. Additionally, the
\texttt{InpatientService} feature was also considered important in predicting
the class, a finding that was also noted by Lucas et al. \cite{Lucas2009},
although they considered the classification of LOS $\leq$ and $>$ 3 days.

>>>>

Recall that $k$-NN with 1 nearest neighbour and C4.5 wrapper feature
selection produced the best accuracy (77.81\%) for the trauma data set, and
logistic regression with correlation coefficient feature selection at a
threshold of 0.1 gave the best AUC (0.846). These two feature selection
methods selected 11 and 29 features respectively, and the features that
were chosen in common between them were: \texttt{operation}, \texttt{bp},
\texttt{iss}, \texttt{lowerlimbnopelvis}, \texttt{age}, \texttt{lowerlimbany}
and \texttt{icu}. This adds evidence to the work of Dinh et al. who found
that \texttt{iss}, \texttt{age} and \texttt{operation} were important
distinguishers of LOS ``less than or equal to 2 days'' or ``greater than 2 days'' \cite{Dinh2013a}. We also
confirm the findings of Gabbe et al. who found that \texttt{age},
\texttt{iss} and \texttt{bp} were useful in predicting the length of
hospital stay of blunt trauma patients \cite{Gabbe2005}. Our feature
selection results also
support the findings of McGonigal et al. \cite{McGonigal1993} who used
\texttt{age} and
\texttt{iss} to predict the probability of survival for trauma patients, a
related problem in the same medical domain.
Our observations suggest the use of feature selection not only as a
pre-processing step to improve the accuracy or AUC of a classifier, but also
as a tool used separately that could help extract insights from medical data.

@@

There are a number of results which are notable, however. Logistic regression
and K*
were still able to achieve a mean AUC of 0.994 with features selected using
information gain at a 0.05 threshold. This meant that it only used 8 out of
the original 14 features, cutting down the number of features by nearly half.
We mentioned that the MLP had the highest discriminating ability when used with
CFS and C4.5 wrapper selection, with AUC 0.983 and 0.992 respectively. While
this is not as high as the best result of 0.994, it is worth pointing out that
CFS and C4.5 selected only selected 2 and 4 features, respectively. This means that
using only 2 features, we were still able to discriminate between the two LOS
classes almost as well as if we used all of the features. Moreover, using
only 6 out of 14 features and $k$-NN with 1 or 20 nearest neighbours, we can
still achieve an accuracy that is less than 1\% worse than the best result
of 98.23\%.

@@

Out of all four automatic feature selection methods, the single feature that
was deemed to be the most important in predicting LOS was \texttt{EpisodeType}.
Although this was a general hospital-wide data set, the importance of this
attribute indicates that condition-specific factors should be taken into
account when predicting the LOS for any medical domain. Additionally, the
\texttt{InpatientService} feature was also considered important in predicting
the class, a finding that was also noted by Lucas et al. \cite{Lucas2009},
although they considered the classification of LOS less than and greater than
3 days.
